Submission and Formatting Instructions for \\ International Conference on Machine Learning (ICML 2019)

### 2019-04-24 paper/icml_ai4good/main.tex
next update - sorry had an unexpected delay

All of the above limitations require contemporary malaria epidemiology simulators to employ stochastic modeling techniques, which negotiate data scarcity and model uncertainty through the use of appropriate prior distributions that can be tuned even from small samples of field data. The population dynamics of groups of typically several thousand hosts are then initialised by sampling from the initial distributionsm, using initial random seeds. Forward simulation then proceeds by rolling out simulation dynamics over time. Policymakers then take interest in comparing simulation outcomes of cherry-picked scenarios and interventions with those of suitably chosen control groups.

@@

However valuable forward simulations of epidemiology scenarios are, the holy grail of goal-driven policymaking lies ultimately in the inverse problem: Given a desired outcome, we wish to find the optimal respective intervention policy given a specific regional context. Due to computational constraints, even an approximate search over the whole simulator input space usually proves intractable.

@@

<Section about prob prog inference, with reference to SHERPA>

>>>>

All of the above limitations require contemporary malaria epidemiology simulators to employ stochastic modeling techniques, which negotiate data scarcity and model uncertainty through the use of appropriate prior distributions that can be tuned even from small samples of field data. The population dynamics of groups of typically several thousand hosts are then initialised by sampling from the initial distributions, using initial random seeds. Forward simulation then proceeds by rolling out population dynamics over time. Simulation outcomes of cherry-picked scenarios and interventions of interest are then compared to suitably designed control runs.

@@

However valuable forward simulations of epidemiology scenarios are, the holy grail of goal-driven policymaking ultimately lies in solving the inverse problem: Given a desired outcome and regional context, identify the series of interventions that will best reach the desired target after a given amount of time. Due to computational constraints, even an approximate search over the whole simulator input space usually proves intractable. An experience-guided search over the simulation output of a small set of manually-designed scenarios of interest therefore long seemed the only feasible way of investigating implications of policy interventions.

Recent work by \citep{Baydin} introduces a fundamental paradigm change that, for the first time, allows to tackle this inverse problem in a way that .

@@

% <Section about prob prog inference, with reference to SHERPA>
